### 2018-12-28 README.Rmd
update pkgdown
try white-on-green logo
patch ids ordering
also updates pkgdown

@@

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# taxadb

@@

```{r include=FALSE}
taxadb:::td_disconnect()
```

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
taxadb:::td_disconnect()
MonetDBLite::monetdblite_shutdown()
```

# taxadb  <img src="man/figures/logo.svg" align="right" alt="" width="120" />

@@

@@

```{r include=FALSE}
taxadb:::td_disconnect()
MonetDBLite::monetdblite_shutdown()
```
